Paper Report

### 2017-12-13 Paper_report.tex
New papers
Save

@@

	\begin{itemize}
	\item $s_{NN}(a|e, f)$ is the score of an alignment based on the source and target sentence.
	\item $f_{a_{i}}$ represents not only this word but the context around this word. Surrounding words of both source and target word are input of DNN, which is handling the context of both sides. This could reduce the explosion of parameter number. \\ In this case, they use fixed length windows surrounding both $e_{i}$ and $f_{j}$. 
	\item $t_{lex}$: Lexical translation score.
	\begin{equation}
	t_{lex}(e_{i},f_{j}|e,f) = functions_{NN}(window(e_{i}),window(f_{j}) )
	\label{Yang13word Lexical Translation Score}
	\end{equation}
	\item $t_{d}$: Distortion score.
	\begin{equation}
	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1}|window(f_{a_{i-1}})) = functions_{NN}(window(f_{a_{i-1}}))
	\end{equation}
	They recognize that this lexicalized distortion does not produce a better alignment. They reverse to the simple version.
	\begin{equation}
	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1})
	\end{equation}
	\end{itemize}

@@

\begin{equation}
s_{NN}(a_1^ J|e_1^ I, f_1^ J) = \prod_{j = 1}^{J} t_{RNN}(a_{j}|a_1^{j-1},e_{a_{j}},f_j  )
\end{equation}

@@

@@

\section{Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation}

@@

\begin{equation}
\end{equation}

@@

\subsection{Hidden Markov Alignment Model \cite{Och2003Systematic}}
The alignment model is re-structured:
\begin{equation}
p(f_1^J, a_1^J|e_1^I) = p(J|e_1^I) \prod_{j=1}^J p(f_j, a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
\end{equation}
\begin{equation}
= p(J|e_1^I) \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
\end{equation}

@@

\paragraph{How to apply NN ?}
\begin{itemize}
\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities for all source-language vocabulary.
\item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
\item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
\end{itemize}

@@

@@

\section{Techniques in Alignment}

\subsection{Agreement between models}

>>>>

%----------------------------------------------------------------------------------------
%	Confidence through Attention
%----------------------------------------------------------------------------------------

@@

	\begin{itemize}
	\item $s_{NN}(a|e, f)$ is the score of an alignment based on the source and target sentence.
	\item $f_{a_{i}}$ represents not only this word but the context around this word. Surrounding words of both source and target word are input of DNN, which is handling the context of both sides. This could reduce the explosion of parameter number. \\ In this case, they use fixed length windows surrounding both $e_{i}$ and $f_{j}$. 
	\item $t_{lex}$: Lexical translation score.
	\begin{equation}
	t_{lex}(e_{i},f_{j}|e,f) = functions_{NN}(window(e_{i}),window(f_{j}) )
	\label{Yang13word Lexical Translation Score}
	\end{equation}
	\item $t_{d}$: Distortion score.
	\begin{equation}
	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1}|window(f_{a_{i-1}})) = functions_{NN}(window(f_{a_{i-1}}))
	\end{equation}
	They recognize that this lexicalized distortion does not produce a better alignment. They reverse to the simple version.
	\begin{equation}
	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1})
	\label{Yang13word Alignment Translation Score}
	\end{equation}
	\end{itemize}

@@

\begin{equation}
s_{NN}(a_1^ J|e_1^ I, f_1^ J) = \prod_{j = 1}^{J} t_{RNN}(a_{j}|a_1^{j-1},e_{a_{j}},f_j  )
\label{Tamura14recurrent Alignment score}
\end{equation}

@@

%----------------------------------------------------------------------------------------
%	Alignment-based Neural Machine Translation
%----------------------------------------------------------------------------------------

\section{Alignment-based Neural Machine Translation \citep{Alkhouli2016AlignmentBasedNM} }

@@

\section{Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation \citep{Wang2017HybridNN} }
The main idea is using NN for both alignment and lexicon model of HMM. These two models are trained jointly using the Baum-Welch algorithm.

The experiment is not for word-based alignment but phrase-based translation, which increases 1\% of BLEU score.

\subsection{NN-based Alignment and Lexical model}
They define the alignment $b_{i} = i \rightarrow j $ (Not $a_{j} = j \rightarrow i $). Review the equation \eqref{Hidden Markov Alignment Model p(f, a|e)}. \\
$p(e_1^I, b_1^I|f_1^J) = \prod_{i=1}^I p(e_i, b_i | b_1^{i-1}, e_1^{i-1}, f_1^J)
$\\
$ = \prod_{i=1}^I p( e_i | e_1^{i-1}, b_1^i, f_1^J) * p( b_i |b_1^{i-1}, e_1^{i-1}, f_1^J)
$

\begin{itemize}
\item Alignment model: $p( b_i |b_1^{i-1}, e_1^{i-1},  f_1^J) = p(b_i - b_{i-1}| f^{b_{i-1} + \gamma m}_{b_{i-1} - \gamma m}, e_{i-n}^{i-1})$ \\
where $\gamma m = \dfrac{m-1}{2}$ and n, m indicate window size.\\
\marginpar{See Figure 1 in \citep{Wang2017HybridNN}}
This lexical alignment model uses the context of $f^{b_{i-1}}$ and $e_i$.

\item Lexical model: $p( e_i | e_1^{i-1}, b_1^{i}, f_1^J) = p(e_i|f^{b_{i} + \gamma m}_{b_{i} - \gamma m}, e_{i-n}^{i-1}  )$\\
$= p(e_i| \: c(e_i),f^{b_{i} + \gamma m}_{b_{i} - \gamma m}, e_{i-n}^{i-1}) * p(c(e_i)|f^{b_{i} + \gamma m}_{b_{i} - \gamma m}, e_{i-n}^{i-1})$\\
For this case, they apply class-factored output layer consisting a class layer (Class probability) and a word layer (Word probability for each class), which reduces the problem of large vocabulary. The word class is applied to target language $e$.
\end{itemize}

I rewrite under the notation of $a_{j}$.
Review the equation \eqref{Hidden Markov Alignment Model p(f, a|e)}. \\
$p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j, a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
$\\
$ = \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j |a_1^{j-1}, f_1^{j-1},  e_1^I)
$

\begin{itemize}
\item Alignment model: $p( a_j |a_1^{j-1}, f_1^{j-1},  e_1^I) = p(a_j - a_{j-1}| e^{a_{j-1} + \gamma m}_{a_{j-1} - \gamma m}, f_{j-n}^{j-1})$ \\
This lexical alignment model uses the context of $e^{a_{j-1}}$ and $f_j$.

\item Lexical model: $p( f_j | f_1^{j-1}, a_j, e_1^I) = p(f_j|e^{a_{j} + \gamma m}_{a_{j} - \gamma m}, f_{j-n}^{j-1})  )$
\marginpar{Class-factored output layer for target or source language ?}
\end{itemize}

\subsection{Objective function}

\subsection{Algorithm}

%----------------------------------------------------------------------------------------
%	HMM Word and Phrase Alignment for Statistical Machine Translation
%----------------------------------------------------------------------------------------

\section{HMM Word and Phrase Alignment for Statistical Machine Translation \citep{Deng2008HMM} }

%----------------------------------------------------------------------------------------
%	Neural Network-based Word Alignment through Score Aggregation
%----------------------------------------------------------------------------------------
\section{Neural Network-based Word Alignment through Score Aggregation \citep{Legrand16neural}}

@@

\begin{equation}
p(f_1^J|e_1^I) = \sum_{a_1^J} p(f_1^J, a_1^J|e_1^I)
\end{equation}

@@

\subsection{Hidden Markov Alignment Model \cite{Och2003Systematic}}
The alignment model is re-structured:
\begin{equation}
p(f_1^J, a_1^J|e_1^I) = p(J|e_1^I) \prod_{j=1}^J p(f_j, a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
\end{equation}
\begin{equation}
= p(J|e_1^I) \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
\label{Hidden Markov Alignment Model p(f, a|e)}
\end{equation}

@@

\paragraph{How to apply NN ?}
\begin{itemize}
\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities for all source-language vocabulary.
\item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.

\item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
\end{itemize}

@@

\subsection{NN-based Alignment under jump-distance approach}
\cite{Yang13word} recognize that the lexicalized distortion does not produce better alignment over the simple jump-distance based model (Not NN, randomly created), based on their experiment of small data. Therefore, they do not use target-language or source-language word for alignment. $t(a_{j}, a_{j-1}|e,f) = t(a_{j} - a_{j-1})$\\
\marginpar{ See \eqref{Yang13word Alignment Translation Score} }

\citep{Tamura14recurrent} continue the work of \citep{Yang13word} but reuse lexicalized distortion combined with RNN.
$t(a_{j}, a_{j-1}|e,f) = t_{RNN}(a_{j} - a_{j-1}| a_{1}^{j-1}, f_j, e_{a_j})$\\
\marginpar{See \eqref{Tamura14recurrent Alignment score}}
One point important is that there is a different set of parameter for each distance.\\

\citep{Alkhouli2016AlignmentBasedNM}, \citep{Wang2017HybridNN} use the context of $f_j$ and $e_{a_j}$. They do not use RNN, just simple FFNN.
$p( a_j, a_{j-1}| f,  e) = p(a_{j} - a_{j-1}| e^{a_{j-1} + \gamma m}_{a_{j-1} - \gamma m}, f_{j-n}^{j-1})$ where $\gamma$, $n$ are window sizes.

@@

\section{Techniques in Alignment}
\subsection{Agreement between models}

\subsection{Word class for large vocabulary}
